Examining Programming Students’ Interaction with Generative AI: A Metacognitive Perspective

### 2024-10-10 CSEDU2025/Paper.tex
update

Spacing, a well-established learning strategy \citep{Carvalho20}, was analyzed
by examining the time intervals between user interactions with CharlieBot.
Approximately 26.2\% of the conversations, or roughly a quarter, included pauses
longer than 60 minutes. However, this data only indicates that students paused
their use of the AI, which could suggest that they were either reflecting on the
topic independently or engaging in unrelated activities. Furthermore, 16.7\%
of the conversations exhibited pauses of 12 hours and 9\% showed delays
exceeding 24 hours between messages, indicating that some degree of spacing
occurred. However, it is important to note that this behavior may have been
influenced by the design of the initial version of CharlieBot, which only kept
the chat session active as long as the student kept the browser tab open and
avoided reloading the page. This adds uncertainty about the precise context in
which students applied spacing.

@@

\subsection{Interleaving}

@@

Intervealing is a learning strategy that involves mixing or alternating
different topics or problems within a single learning session. This approach has
been shown to be useful for promoting long-term learning and improving the
application of knowledge in other situations \citep{Rivers21}.

>>>>

Approximately 26.2\% of the conversations, or roughly a quarter, included pauses
longer than 60 minutes. However, this data only indicates that students paused
their use of the AI, which could suggest that they were either reflecting on the
topic independently or engaging in unrelated activities. Furthermore, 16.7\%
of the conversations exhibited pauses of 12 hours and 9\% showed delays
exceeding 24 hours between messages, indicating that some degree of spacing
occurred. However, it is important to note that this behavior may have been
influenced by the design of the initial version of CharlieBot, which only kept
the chat session active as long as the student kept the browser tab open and
avoided reloading the page. This adds uncertainty about the precise context in
which students applied spacing.

@@

\subsection{Perspective Interleaving}

@@
